\chapter{ Lady~Susan Vernon to Mr~Vernon}
	
	\begin{a4}
	\vspace{5em}
	\end{a4}
  \begin{mail}{Langford, Dec.}{My dear Brother,} 
I can no longer refuse myself the pleasure of profiting by your kind invitation when we last parted of spending some weeks with you at Churchhill, and, therefore, if quite convenient to you and Mrs~Vernon to receive me at present, I shall hope within a few days to be introduced to a sister whom I have so long desired to be acquainted with. My kind friends here are most affectionately urgent with me to prolong my stay, but their hospitable and cheerful dispositions lead them too much into society for my present situation and state of mind; and I impatiently look forward to the hour when I shall be admitted into your delightful retirement.

I long to be made known to your dear little children, in whose hearts I shall be very eager to secure an interest. I shall soon have need for all my fortitude, as I am on the point of separation from my own daughter. The long illness of her dear father prevented my paying her that attention which duty and affection equally dictated, and I have too much reason to fear that the governess to whose care I consigned her was unequal to the charge. I have therefore resolved on placing her at one of the best private schools in town, where I shall have an opportunity of leaving her myself in my way to you. I am determined, you see, not to be denied admittance at Churchhill. It would indeed give me most painful sensations to know that it were not in your power to receive me. 
\closeletter[Your most obliged and affectionate sister,]{S. Vernon}
\end{mail}