\chapter{Mr~De Courcy to Mrs~Vernon}
	
	\begin{mail}{Parklands.}{My dear Sister,}
I congratulate you and Mr~Vernon on being about to receive into your family the most accomplished coquette in England. As a very distinguished flirt I have always been taught to consider her, but it has lately fallen in my way to hear some particulars of her conduct at Langford: which prove that she does not confine herself to that sort of honest flirtation which satisfies most people, but aspires to the more delicious gratification of making a whole family miserable. By her behaviour to Mr~Mainwaring she gave jealousy and wretchedness to his wife, and by her attentions to a young man previously attached to Mr~Mainwaring's sister deprived an amiable girl of her lover.

I learnt all this from Mr~Smith, now in this neighbourhood (I have dined with him, at Hurst and Wilford), who is just come from Langford where he was a fortnight with her ladyship, and who is therefore well qualified to make the communication.

What a woman she must be! I long to see her, and shall certainly accept your kind invitation, that I may form some idea of those bewitching powers which can do so much—engaging at the same time, and in the same house, the affections of two men, who were neither of them at liberty to bestow them—and all this without the charm of youth! I am glad to find Miss~Vernon does not accompany her mother to Churchhill, as she has not even manners to recommend her; and, according to Mr~Smith's account, is equally dull and proud. Where pride and stupidity unite there can be no dissimulation worthy notice, and Miss~Vernon shall be consigned to unrelenting contempt; but by all that I can gather Lady~Susan possesses a degree of captivating deceit which it must be pleasing to witness and detect. I shall be with you very soon, and am ever, 
\closeletter[Your affectionate brother,]{R. De Courcy.} 
\end{mail}