\chapter{Lady~De Courcy to Mrs~Vernon}
  
  \begin{mail}{Parklands.}{My dear Catherine,}

Unluckily I was confined to my room when your last letter came, by a cold which affected my eyes so much as to prevent my reading it myself, so I could not refuse your father when he offered to read it to me, by which means he became acquainted, to my great vexation, with all your fears about your brother. I had intended to write to Reginald myself as soon as my eyes would let me, to point out, as well as I could, the danger of an intimate acquaintance, with so artful a woman as Lady~Susan, to a young man of his age, and high expectations. I meant, moreover, to have reminded him of our being quite alone now, and very much in need of him to keep up our spirits these long winter evenings. Whether it would have done any good can never be settled now, but I am excessively vexed that Sir~Reginald should know anything of a matter which we foresaw would make him so uneasy. He caught all your fears the moment he had read your letter, and I am sure he has not had the business out of his head since. He wrote by the same post to Reginald a long letter full of it all, and particularly asking an explanation of what he may have heard from Lady~Susan to contradict the late shocking reports. His answer came this morning, which I shall enclose to you, as I think you will like to see it. I wish it was more satisfactory; but it seems written with such a determination to think well of Lady~Susan, that his assurances as to marriage, \&c., do not set my heart at ease. I say all I can, however, to satisfy your father, and he is certainly less uneasy since Reginald's letter. How provoking it is, my dear Catherine, that this unwelcome guest of yours should not only prevent our meeting this Christmas, but be the occasion of so much vexation and trouble! Kiss the dear children for me. 

\closeletter[Your affectionate mother,]{C. De Courcy.} 
\end{mail}