\chapter{Lady~Susan to Mrs~Johnson}
  
  \begin{mail}{Churchhill.}{}
  
Never, my dearest Alicia, was I so provoked in my life as by a letter this morning from Miss~Summers. That horrid girl of mine has been trying to run away. I had not a notion of her being such a little devil before, she seemed to have all the Vernon milkiness; but on receiving the letter in which I declared my intention about Sir~James, she actually attempted to elope; at least, I cannot otherwise account for her doing it. She meant, I suppose, to go to the Clarkes in Staffordshire, for she has no other acquaintances. But she shall be punished, she shall have him. I have sent Charles to town to make matters up if he can, for I do not by any means want her here. If Miss~Summers will not keep her, you must find me out another school, unless we can get her married immediately. Miss~S. writes word that she could not get the young Lady~to assign any cause for her extraordinary conduct, which confirms me in my own previous explanation of it. Frederica is too shy, I think, and too much in awe of me to tell tales, but if the mildness of her uncle should get anything out of her, I am not afraid. I trust I shall be able to make my story as good as hers. If I am vain of anything, it is of my eloquence. Consideration and esteem as surely follow command of language as admiration waits on beauty, and here I have opportunity enough for the exercise of my talent, as the chief of my time is spent in conversation.

Reginald is never easy unless we are by ourselves, and when the weather is tolerable, we pace the shrubbery for hours together. I like him on the whole very well; he is clever and has a good deal to say, but he is sometimes impertinent and troublesome. There is a sort of ridiculous delicacy about him which requires the fullest explanation of whatever he may have heard to my disadvantage, and is never satisfied till he thinks he has ascertained the beginning and end of everything. This is one sort of love, but I confess it does not particularly recommend itself to me. I infinitely prefer the tender and liberal spirit of Mainwaring, which, impressed with the deepest conviction of my merit, is satisfied that whatever I do must be right; and look with a degree of contempt on the inquisitive and doubtful fancies of that heart which seems always debating on the reasonableness of its emotions. Mainwaring is indeed, beyond all compare, superior to Reginald—superior in everything but the power of being with me! Poor fellow! he is much distracted by jealousy, which I am not sorry for, as I know no better support of love. He has been teazing me to allow of his coming into this country, and lodging somewhere near \textit{incog}.; but I forbade everything of the kind. Those women are inexcusable who forget what is due to themselves, and the opinion of the world. 

\closeletter[Yours ever,]{S. Vernon.} 
\end{mail}