\chapter{From the same to the same}
  
  \begin{mail}{Churchhill.}{My dear Mother,}

I am very glad to find that my description of Frederica Vernon has interested you, for I do believe her truly deserving of your regard; and when I have communicated a notion which has recently struck me, your kind impressions in her favour will, I am sure, be heightened. I cannot help fancying that she is growing partial to my brother. I so very often see her eyes fixed on his face with a remarkable expression of pensive admiration. He is certainly very handsome; and yet more, there is an openness in his manner that must be highly prepossessing, and I am sure she feels it so. Thoughtful and pensive in general, her countenance always brightens into a smile when Reginald says anything amusing; and, let the subject be ever so serious that he may be conversing on, I am much mistaken if a syllable of his uttering escapes her. I want to make him sensible of all this, for we know the power of gratitude on such a heart as his; and could Frederica's artless affection detach him from her mother, we might bless the day which brought her to Churchhill. I think, my dear mother, you would not disapprove of her as a daughter. She is extremely young, to be sure, has had a wretched education, and a dreadful example of levity in her mother; but yet I can pronounce her disposition to be excellent, and her natural abilities very good. Though totally without accomplishments, she is by no means so ignorant as one might expect to find her, being fond of books and spending the chief of her time in reading. Her mother leaves her more to herself than she did, and I have her with me as much as possible, and have taken great pains to overcome her timidity. We are very good friends, and though she never opens her lips before her mother, she talks enough when alone with me to make it clear that, if properly treated by Lady~Susan, she would always appear to much greater advantage. There cannot be a more gentle, affectionate heart; or more obliging manners, when acting without restraint; and her little cousins are all very fond of her. 

\closeletter[Your affectionate daughter,]{C. Vernon.} 
\end{mail}