\chapter{Mrs~Vernon to Lady~De Courcy}
  
  \begin{mail}{Churchhill.}{}

This letter, my dear Mother, will be brought you by Reginald. His long visit is about to be concluded at last, but I fear the separation takes place too late to do us any good. She is going to London to see her particular friend, Mrs~Johnson. It was at first her intention that Frederica should accompany her, for the benefit of masters, but we overruled her there. Frederica was wretched in the idea of going, and I could not bear to have her at the mercy of her mother; not all the masters in London could compensate for the ruin of her comfort. I should have feared, too, for her health, and for everything but her principles—there I believe she is not to be injured by her mother, or her mother's friends; but with those friends she must have mixed (a very bad set, I doubt not), or have been left in total solitude, and I can hardly tell which would have been worse for her. If she is with her mother, moreover, she must, alas! in all probability be with Reginald, and that would be the greatest evil of all. Here we shall in time be in peace, and our regular employments, our books and conversations, with exercise, the children, and every domestic pleasure in my power to procure her, will, I trust, gradually overcome this youthful attachment. I should not have a doubt of it were she slighted for any other woman in the world than her own mother. How long Lady~Susan will be in town, or whether she returns here again, I know not. I could not be cordial in my invitation, but if she chuses to come no want of cordiality on my part will keep her away. I could not help asking Reginald if he intended being in London this winter, as soon as I found her ladyship's steps would be bent thither; and though he professed himself quite undetermined, there was something in his look and voice as he spoke which contradicted his words. I have done with lamentation; I look upon the event as so far decided that I resign myself to it in despair. If he leaves you soon for London everything will be concluded. 

\closeletter[Your affectionate, \&c.,]{C. Vernon.} 
\end{mail}