\chapter{Lady~Susan Vernon to Mrs~Johnson}
  
  \begin{mail}{Upper Seymour Street.}{My dear Alicia,}
  
 There needed not this last fit of the gout to make me detest Mr~Johnson, but now the extent of my aversion is not to be estimated. To have you confined as nurse in his apartment! My dear Alicia, of what a mistake were you guilty in marrying a man of his age! just old enough to be formal, ungovernable, and to have the gout; too old to be agreeable, too young to die. I arrived last night about five, had scarcely swallowed my dinner when Mainwaring made his appearance. I will not dissemble what real pleasure his sight afforded me, nor how strongly I felt the contrast between his person and manners and those of Reginald, to the infinite disadvantage of the latter. For an hour or two I was even staggered in my resolution of marrying him, and though this was too idle and nonsensical an idea to remain long on my mind, I do not feel very eager for the conclusion of my marriage, nor look forward with much impatience to the time when Reginald, according to our agreement, is to be in town. I shall probably put off his arrival under some pretence or other. He must not come till Mainwaring is gone. I am still doubtful at times as to marrying; if the old man would die I might not hesitate, but a state of dependance on the caprice of Sir~Reginald will not suit the freedom of my spirit; and if I resolve to wait for that event, I shall have excuse enough at present in having been scarcely ten months a widow. I have not given Mainwaring any hint of my intention, or allowed him to consider my acquaintance with Reginald as more than the commonest flirtation, and he is tolerably appeased. Adieu, till we meet; I am enchanted with my lodgings. 

\closeletter[Yours ever,]{S. Vernon.} 
\end{mail}