\chapter{Mrs~Johnson to Lady~Susan}
  
  	\begin{a4}
	\vspace{5em}
	\end{a4}
	
  \begin{mail}{Edward Street.}{My dear Creature,}
 
 I am in agonies, and know not what to do. Mr~De Courcy arrived just when he should not. Mrs~Mainwaring had that instant entered the house, and forced herself into her guardian's presence, though I did not know a syllable of it till afterwards, for I was out when both she and Reginald came, or I should have sent him away at all events; but she was shut up with Mr~Johnson, while he waited in the drawing-room for me. She arrived yesterday in pursuit of her husband, but perhaps you know this already from himself. She came to this house to entreat my husband's interference, and before I could be aware of it, everything that you could wish to be concealed was known to him, and unluckily she had wormed out of Mainwaring's servant that he had visited you every day since your being in town, and had just watched him to your door herself! What could I do! Facts are such horrid things! All is by this time known to De Courcy, who is now alone with Mr~Johnson. Do not accuse me; indeed, it was impossible to prevent it. Mr~Johnson has for some time suspected De Courcy of intending to marry you, and would speak with him alone as soon as he knew him to be in the house. That detestable Mrs~Mainwaring, who, for your comfort, has fretted herself thinner and uglier than ever, is still here, and they have been all closeted together. What can be done? At any rate, I hope he will plague his wife more than ever. With anxious wishes, 

\closeletter[Yours faithfully,]{Alicia.} 
\end{mail}