\chapter{Mr~De Courcy to Lady~Susan}
  
  \begin{mail}{\doubleemdash  Hotel.}{}

Why would you write to me? Why do you require particulars? But, since it must be so, I am obliged to declare that all the accounts of your misconduct during the life, and since the death of Mr~Vernon, which had reached me, in common with the world in general, and gained my entire belief before I saw you, but which you, by the exertion of your perverted abilities, had made me resolved to disallow, have been unanswerably proved to me; nay more, I am assured that a connection, of which I had never before entertained a thought, has for some time existed, and still continues to exist, between you and the man whose family you robbed of its peace in return for the hospitality with which you were received into it; that you have corresponded with him ever since your leaving Langford; not with his wife, but with him, and that he now visits you every day. Can you, dare you deny it? and all this at the time when I was an encouraged, an accepted lover! From what have I not escaped! I have only to be grateful. Far from me be all complaint, every sigh of regret. My own folly had endangered me, my preservation I owe to the kindness, the integrity of another; but the unfortunate Mrs~Mainwaring, whose agonies while she related the past seemed to threaten her reason, how is \textit{she} to be consoled! After such a discovery as this, you will scarcely affect further wonder at my meaning in bidding you adieu. My understanding is at length restored, and teaches no less to abhor the artifices which had subdued me than to despise myself for the weakness on which their strength was founded. 

\closeletter{R. De Courcy.}
\end{mail}