\chapter{Mrs~Johnson to Lady~Susan Vernon}
  
  \begin{mail}{Edward Street}{}

I am grieved, though I cannot be astonished at your rupture with Mr~De Courcy; he has just informed Mr~Johnson of it by letter. He leaves London, he says, to-day. Be assured that I partake in all your feelings, and do not be angry if I say that our intercourse, even by letter, must soon be given up. It makes me miserable; but Mr~Johnson vows that if I persist in the connection, he will settle in the country for the rest of his life, and you know it is impossible to submit to such an extremity while any other alternative remains. You have heard of course that the Mainwarings are to part, and I am afraid Mrs~M. will come home to us again; but she is still so fond of her husband, and frets so much about him, that perhaps she may not live long. Miss~Mainwaring is just come to town to be with her aunt, and they say that she declares she will have Sir~James Martin before she leaves London again. If I were you, I would certainly get him myself. I had almost forgot to give you my opinion of Mr~De Courcy; I am really delighted with him; he is full as handsome, I think, as Mainwaring, and with such an open, good-humoured countenance, that one cannot help loving him at first sight. Mr~Johnson and he are the greatest friends in the world. Adieu, my dearest Susan, I wish matters did not go so perversely. That unlucky visit to Langford! but I dare say you did all for the best, and there is no defying destiny. 

\closeletter[Your sincerely attached,]{Alicia.} 
\end{mail}