\chapter{Lady~Susan to Mrs~Johnson}
  
  \begin{mail}{Upper Seymour Street.}{My dear Alicia,}
  
I yield to the necessity which parts us. Under such circumstances you could not act otherwise. Our friendship cannot be impaired by it, and in happier times, when your situation is as independent as mine, it will unite us again in the same intimacy as ever. For this I shall impatiently wait, and meanwhile can safely assure you that I never was more at ease, or better satisfied with myself and everything about me than at the present hour. Your husband I abhor, Reginald I despise, and I am secure of never seeing either again. Have I not reason to rejoice? Mainwaring is more devoted to me than ever; and were we at liberty, I doubt if I could resist even matrimony offered by \textit{him}. This event, if his wife live with you, it may be in your power to hasten. The violence of her feelings, which must wear her out, may be easily kept in irritation. I rely on your friendship for this. I am now satisfied that I never could have brought myself to marry Reginald, and am equally determined that Frederica never \textit{shall}. To-morrow, I shall fetch her from Churchhill, and let Maria Mainwaring tremble for the consequence. Frederica shall be Sir~James's wife before she quits my house, and \textit{she} may whimper, and the Vernons may storm, I regard them not. I am tired of submitting my will to the caprices of others; of resigning my own judgment in deference to those to whom I owe no duty, and for whom I feel no respect. I have given up too much, have been too easily worked on, but Frederica shall now feel the difference. Adieu, dearest of friends; may the next gouty attack be more favourable! and may you always regard me as unalterably yours, 
\closeletter{S. Vernon.} 
\end{mail}