\chapter{Lady~De Courcy to Mrs~Vernon}
  
  	
	\begin{a4}
	\vspace{5em}
	\end{a4}
	
	  	\begin{letter}
\enlargethispage{\baselineskip}
\end{letter}
	
  \begin{mail}{}{My dear Catherine,}

I have charming news for you, and if I had not sent off my letter this morning you might have been spared the vexation of knowing of Reginald's being gone to London, for he is returned. Reginald is returned, not to ask our consent to his marrying Lady~Susan, but to tell us they are parted for ever. He has been only an hour in the house, and I have not been able to learn particulars, for he is so very low that I have not the heart to ask questions, but I hope we shall soon know all. This is the most joyful hour he has ever given us since the day of his birth. Nothing is wanting but to have you here, and it is our particular wish and entreaty that you would come to us as soon as you can. You have owed us a visit many long weeks; I hope nothing will make it inconvenient to Mr~Vernon; and pray bring all my grand-children; and your dear niece is included, of course; I long to see her. It has been a sad, heavy winter hitherto, without Reginald, and seeing nobody from Churchhill. I never found the season so dreary before; but this happy meeting will make us young again. Frederica runs much in my thoughts, and when Reginald has recovered his usual good spirits (as I trust he soon will) we will try to rob him of his heart once more, and I am full of hopes of seeing their hands joined at no great distance. 

\closeletter[Your affectionate mother,]{C. De Courcy.} 
\end{mail}